---
title: "National Weather Service API"
author: "Daniel E. Weeks"
date: "`r format(Sys.time(), '%B %d, %Y, %R')`"
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  pdf_document:
    toc: true
    number_sections: true
    toc_depth: 3
  html_document:
    df_print: paged
    toc: true
    number_sections: true
    toc_depth: '3'
    code_folding: show
#   md_extensions: +raw_attribute
---

```{r,echo=FALSE,message=FALSE,warning=FALSE}
require(knitr)
# Set so that long lines in R will be wrapped:
opts_chunk$set(tidy.opts=list(width.cutoff=80),tidy=TRUE)
```

```{r,echo=FALSE}
# In the event of a crash, save the working space on exit:
save_all <- function() {
  save.image("recover.RData")
}
options(error = save_all)
```


# Load Libraries

```{r load_libraries,message=FALSE}
library(tidyverse)
library(tidylog)
library(jsonlite)
library(httr)
library(zipcodeR)
library(zipcode)
library(scales)
library(lutz)
library(ggExtra)
library(patchwork)
library(lubridate)
library(ggrepel)
```

# Input directory and files 

```{r}
# Print the working directory
getwd()
```
The input files used in this analysis are ... and can be found in ... 

# Functions

## coord_y_datetime

From https://stackoverflow.com/questions/43625341/reverse-datetime-posixct-data-axis-in-ggplot

```{r}
coord_y_datetime <- function(xlim = NULL, ylim = NULL, expand = TRUE) {
  if (!is.null(ylim)) {
    ylim <- lubridate::as_datetime(ylim)
  }
  ggplot2::coord_cartesian(xlim = xlim, ylim = ylim, expand = expand)
}
```

# National Weather Service API

Joe Guiness has a YouTube video that shows how to access the NWS API

https://youtu.be/hxl1c8WRNiA

This code is based on Joe Guiness' YouTube tutorial:

```{r}
# Pittsburgh
lon <- -79.9959
lat <- 40.4406

# Look up latitude and longitude from the zip code
lat.long <- geocode_zip("15217")
lat <- lat.long$lat
lon <- lat.long$lng


# Home: 40 26' 2" N  79 54' 55" W
# 40.43389, -79.91528
lon <- -1* (79 + (54/60) + (55/3600))
lat <- 40 + (26/60) + (2/3600)

# Look up latitude and longitude from the zip code
zip <- 15217
data(zipcode)
lat.long <- zipcode[zipcode$zip==zip,c("latitude","longitude")]
lat <- lat.long[1]
lon <- lat.long[2]

# Home: 40.433810, -79.915280
#       40.433673661058684	-79.91517223628321
#       40.43362	  -79.91536
#       40.4338467, -79.9153318
#       40.43400083686655, -79.91533284458444 <= Google Maps
lon <- -79.91533284458444
lat <- 40.43400083686655



get_NWS_data <- function(lat, lon) {
  myurl <- paste0("https://api.weather.gov/points/",lat,",",lon)
  weather_list <- fromJSON(myurl)
} 

weather_list <- get_NWS_data(lat,lon)

get_forecast <- function(weather_list) {
  sv <- GET(weather_list$properties$forecast)
  forecast <- fromJSON(content(sv, as="text", encoding = "UTF-8"))
  forecast$properties$city <- weather_list$properties$relativeLocation$properties$city
   forecast$properties$state <- weather_list$properties$relativeLocation$properties$state
    forecast$properties$coordinates <- weather_list$properties$relativeLocation$geometry$coordinates
    class(forecast) <- "weather_forecast"
    return(forecast)
}

forecast <- get_forecast(weather_list)


print.weather_forecast <- function(forecast, nperiods = NULL) {
  fdb <- forecast$properties$periods
  if (is.null( nperiods)) {
    nperiods <- nrow(fdb)
  }  
  
  start_times <- fdb$startTime
  start_dates <- as.POSIXct(substr(start_times, 1, 19), format="%FT%T")
  end_times <- fdb$endTime
  end_dates <- as.POSIXct(substr(end_times, 1, 19), format="%FT%T")
  
  st0 <- paste0("Forecast for ", forecast$properties$city,", ",
                forecast$properties$state," (",
                forecast$properties$coordinates[2], ", ",
                forecast$properties$coordinates[1], ")")
  cat(st0,"\n\n")
  
  for (j in 1:nperiods) {
    st1 <- paste0(fdb$name[j]," ", format(start_dates[j], "%F"), ": ",
                  fdb$shortForecast[j],"\n")
                  
    cat(st1)
    if (fdb$isDaytime[j]) {
      prefix <- "High: "
    } else {
      prefix <- "Low: "
    }
    st1b <- paste0(prefix,fdb$temperature[j], " ", fdb$temperatureUnit[j],"; ",
                  fdb$windDirection[j]," winds ", fdb$windSpeed[j] ,"\n")
    cat(st1b)
    st2 <- strsplit( fdb$detailedForecast[j], " ")[[1]]
    cat(st2, fill = TRUE)
    cat("\n")
  }
}
```

## Forecast 

```{r, comment=""}
forecast
```

## Hourly forecast

```{r}
get_hourly_forecast <- function(weather_list) {
  sv <- GET(weather_list$properties$forecastHourly)
  forecast <- fromJSON(content(sv, as="text", encoding = "UTF-8"))
  forecast$properties$city <- weather_list$properties$relativeLocation$properties$city
   forecast$properties$state <- weather_list$properties$relativeLocation$properties$state
    forecast$properties$coordinates <- weather_list$properties$relativeLocation$geometry$coordinates
    class(forecast) <- "hourly_forecast"
    return(forecast)
}

hourly_forecast <- get_hourly_forecast(weather_list)

db <- hourly_forecast$properties$periods
db$Time <- as.POSIXct(db$startTime, format="%FT%T")

tz <- tz_lookup_coords(lat = lat, lon = lon, method = "accurate")

db$NightDay <- as.numeric(db$isDaytime)

db$templab <- as.character(round(db$temperature,0))
db$templab[1:length(db$templab) %% 6 != 1] <- NA

st0 <- paste0("Forecast for ", forecast$properties$city,", ",
                forecast$properties$state," (",
                round(forecast$properties$coordinates[2],3), ", ",
                round(forecast$properties$coordinates[1],3), ")")

db$`wind speed` <- as.numeric(gsub(" mph","",db$windSpeed))
db$windlab <- as.character(db$`wind speed`)
db$windlab[1:length(db$windlab) %% 6 != 1] <- NA
```

## Temperature

### Landscape

```{r}
pTemp <- ggplot(data = db, aes(x=Time, y=temperature, color=NightDay)) + 
  geom_line() + 
  geom_text(aes(y=temperature,label=templab),vjust=-1) +
  scale_x_datetime(labels = date_format("%a %H", tz=tz), breaks="6 hours") +
  xlab("Time") + 
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  theme(legend.position="none") +
  scale_colour_gradient(low="black",high="orange") +
  geom_hline(yintercept = 32, color ="darkblue", lty=2) +
  ggtitle(paste0("Temperature ",st0)) +
  ylim(min(db$temperature),max(db$temperature)+4)

pTemp
```

### Portrait

```{r}
vTemp <- ggplot(data = db, aes(y=Time, x=temperature, color=NightDay)) + 
  geom_path() + 
  geom_text(aes(x=temperature,label=templab),vjust=-1) +
  scale_y_datetime(labels = date_format("%a %H", tz=tz), breaks="6 hours") +
  ylab("Time") + 
  theme(legend.position="none") +
  scale_colour_gradient(low="black",high="orange") +
  geom_vline(xintercept = 32, color ="darkblue", lty=2) +
  ggtitle(paste0("Temperature ",st0)) +
  xlim(min(db$temperature),max(db$temperature)+2) +
  coord_y_datetime(ylim = c(max(db$Time), min(db$Time))) +
  scale_x_continuous(breaks= pretty_breaks())

vTemp
```


## Wind speed

```{r}
pWind <- ggplot(data = db, aes(x=Time, y=`wind speed`, color=NightDay)) + 
  geom_line() + 
  geom_text(aes(y=`wind speed`,label=windlab),vjust=-1) +
  scale_x_datetime(labels = date_format("%a %H", tz=tz), breaks="6 hours") +
  xlab("Time") + 
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  theme(legend.position="none") +
  scale_colour_gradient(low="black",high="orange") +
  ggtitle(paste0("Wind Speed ",st0)) +
  ylim(min(db$`wind speed`),max(db$`wind speed`)+1)

pWind
```

## Grid forecast

```{r}
get_grid_forecast <- function(weather_list) {
  sv <- GET(weather_list$properties$forecastGridData)
  forecast <- fromJSON(content(sv, as="text", encoding = "UTF-8"))
  forecast$properties$city <- weather_list$properties$relativeLocation$properties$city
   forecast$properties$state <- weather_list$properties$relativeLocation$properties$state
    forecast$properties$coordinates <- weather_list$properties$relativeLocation$geometry$coordinates
    class(forecast) <- "hourly_forecast"
    return(forecast)
}

grid_forecast <- get_grid_forecast(weather_list)

db.orig <- db
```

## Barometric Pressure

```{r}
db <- grid_forecast$properties$pressure[[1]]
db$lab <- as.character(db$value)
db$lab[1:length(db$value) %% 6 != 1] <- NA
db <- dplyr::rename(db, Time=validTime, pressure=value)
db$Time <- as.POSIXct(db$Time, format="%FT%T",tz=tz)
```

```{r}
pPressure <- ggplot(data = db, aes(x=Time, y=pressure)) + 
  geom_line() + 
  geom_text(aes(y=pressure,label=lab),vjust=-1) +
  scale_x_datetime(labels = date_format("%a %H", tz=tz), breaks="6 hours") +
  xlab("Time") + 
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  theme(legend.position="none") +
  scale_colour_gradient(low="black",high="orange") +
  ggtitle(paste0("Barometric Pressure ",st0)) +
  ylim(min(db$pressure),max(db$pressure)+0.05)

pPressure
```

## Sky cover

```{r}
db <- grid_forecast$properties$skyCover$values
db$lab <- as.character(db$value)
db$lab[1:length(db$value) %% 6 != 1] <- NA
db <- rename(db, Time=validTime, `sky cover`=value)
db$Time <- as.POSIXct(db$Time, format="%FT%T",tz=tz)
```

### Landscape

```{r}
pSkyCover <- ggplot(data = db, aes(x=Time, y=`sky cover`)) + 
  geom_line() + 
  geom_text(aes(y=`sky cover`,label=lab),vjust=-1) +
  scale_x_datetime(labels = date_format("%a %H", tz=tz), breaks="6 hours") +
  xlab("Time") + 
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  theme(legend.position="none") +
  scale_colour_gradient(low="black",high="orange") +
  ggtitle(paste0("Sky Cover ",st0)) +
  ylim(min(db$`sky cover`),max(db$`sky cover`)+3)

pSkyCover
```

### Tiled heatmap

```{r, fig.width=4}
tmp <- db
tmp$y <- "Sky Cover"
hr <- as.period(ms("60:00"),"hours")
tmp$hj <- rep(c(0.8,0,-0.8), length.out=nrow(db))

hSkyCover <- ggplot(data=tmp, aes(x=y,y=Time,fill=`sky cover`)) + 
  geom_tile(height=3600*6) +
  geom_text_repel(aes(label=lab), size=3, point.size=NA, direction="x", min.segment.length = 10, na.rm=TRUE) +
scale_y_datetime(labels = date_format("%a %H", tz=tz), breaks="6 hours") +
coord_y_datetime(ylim = c(max(tmp$Time), min(tmp$Time))) +
scale_fill_gradient2(low="white", high="darkgray", limits= c(0,100)) +
  theme_minimal() +
  theme(axis.ticks.x=element_blank(),
        axis.title.x = element_blank(),
        axis.line.y = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())

hSkyCover
```


## Probability of precipitation

```{r}
db <- grid_forecast$properties$probabilityOfPrecipitation$values
db$lab <- as.character(db$value)
db$lab[1:length(db$value) %% 4 != 1] <- NA
db <- rename(db, Time=validTime, `precipitation probability`=value)
db$Time <- as.POSIXct(db$Time, format="%FT%T",tz=tz)
```

### Landscape

```{r}
pPrecpProb <- ggplot(data = db, aes(x=Time, y=`precipitation probability`)) + 
  geom_line() + 
  geom_text(aes(y=`precipitation probability`,label=lab),vjust=-1) +
  scale_x_datetime(labels = date_format("%a %H", tz=tz), breaks="6 hours") +
  xlab("Time") + 
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  theme(legend.position="none") +
  scale_colour_gradient(low="black",high="orange") +
  ggtitle(paste0("Precipitation Prob. ",st0)) +
  ylim(min(db$`precipitation probability`),max(db$`precipitation probability`)+3)

pPrecpProb
```

```{r}
coord_y_datetime <- function(xlim = NULL, ylim = NULL, expand = TRUE) {
  if (!is.null(ylim)) {
    ylim <- lubridate::as_datetime(ylim)
  }
  ggplot2::coord_cartesian(xlim = xlim, ylim = ylim, expand = expand)
}
```

### Portrait


```{r}
vPrecpProb <- ggplot(data = db, aes(y=Time, x=`precipitation probability`)) + 
  geom_path() + 
  geom_text(aes(x=`precipitation probability`,label=lab),vjust=-1) +
  scale_y_datetime(labels = date_format("%a %H", tz=tz), breaks="6 hours") +
  ylab("Time") + 
  theme(legend.position="none") +
  scale_colour_gradient(low="black",high="orange") +
  ggtitle(paste0("Precipitation Prob. ",st0)) +
  xlim(min(db$`precipitation probability`),max(db$`precipitation probability`)+3) +
  coord_y_datetime(ylim = c(max(db$Time), min(db$Time))) +
  scale_x_continuous(breaks= pretty_breaks())

vPrecpProb
```

### Tiled heatmap

```{r, fig.width=4, warning=FALSE, message=FALSE}
tmp <- db
tmp$y <- "Precip. Prob."
hr <- as.period(ms("60:00"),"hours")
tmp$hj <- rep(c(0.8,0,-0.8), length.out=nrow(db))

hPrecipProb <- ggplot(data=tmp, aes(x=y,y=Time,fill=`precipitation probability`)) + 
  geom_tile(height=3600*6) +
  geom_text_repel(aes(label=`precipitation probability`), size=3, point.size=NA, direction="x", min.segment.length = 10, na.rm = TRUE, verbose = FALSE) +
scale_y_datetime(labels = date_format("%a %H", tz=tz), breaks="6 hours") +
coord_y_datetime(ylim = c(max(tmp$Time), min(tmp$Time))) +
scale_fill_gradient2(low="gray", high="blue", limits= c(0,100)) +
  theme_minimal() +
  theme(axis.ticks.x=element_blank(),
        axis.title.x = element_blank(),
        axis.line.y = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())

hPrecipProb
```


# Weather

## Forecast

```{r, echo=FALSE, comment=""}
forecast
```

## Temperature

```{r, echo=FALSE, warning=FALSE}
pTemp
```

## Wind Speed

```{r, echo=FALSE, warning=FALSE}
pWind
```

## Barometric Pressure

```{r, echo=FALSE, warning=FALSE}
pPressure
```

## Sky Cover

```{r, echo=FALSE, warning=FALSE}
pSkyCover
hSkyCover
```

## Precipitation Probability

```{r, echo=FALSE, warning=FALSE}
pPrecpProb
hPrecipProb
```

## Combined plots

```{r, echo=FALSE, warning=FALSE}
pTemp / pPrecpProb 
pSkyCover / pPressure 
pWind 
vTemp 
hPrecipProb | hSkyCover 
```


# Session Information

```{r}
sessionInfo()
```

