---
title: "National Weather Service API"
author: "Daniel E. Weeks"
date: "`r format(Sys.time(), '%B %d, %Y, %R')`"
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  pdf_document:
    toc: true
    number_sections: true
    toc_depth: 3
  html_document:
    df_print: paged
    toc: true
    number_sections: true
    toc_depth: '3'
    code_folding: show
#   md_extensions: +raw_attribute
---

```{r,echo=FALSE,message=FALSE,warning=FALSE}
require(knitr)
# Set so that long lines in R will be wrapped:
opts_chunk$set(tidy.opts=list(width.cutoff=80),tidy=TRUE)
```

```{r,echo=FALSE}
# In the event of a crash, save the working space on exit:
save_all <- function() {
  save.image("recover.RData")
}
options(error = save_all)
```


# Load Libraries

```{r load_libraries,message=FALSE}
library(tidyverse)
library(tidylog)
library(jsonlite)
library(httr)
library(zipcodeR)
library(zipcode)
library(scales)
library(lutz)
library(ggExtra)
library(patchwork)
library(lubridate)
library(ggrepel)
library(pander)
library(maptools)
```

# Input directory and files 

```{r}
# Print the working directory
getwd()
```
The input files used in this analysis are ... and can be found in ... 

# Functions

## coord_y_datetime

From https://stackoverflow.com/questions/43625341/reverse-datetime-posixct-data-axis-in-ggplot

```{r}
coord_y_datetime <- function(xlim = NULL, ylim = NULL, expand = TRUE) {
  if (!is.null(ylim)) {
    ylim <- lubridate::as_datetime(ylim)
  }
  ggplot2::coord_cartesian(xlim = xlim, ylim = ylim, expand = expand)
}
```

# National Weather Service API

Joe Guiness has a YouTube video that shows how to access the NWS API

https://youtu.be/hxl1c8WRNiA

This code is based on Joe Guiness' YouTube tutorial:

```{r}
# Oradell
lat <- 40.77322
lon <- -74.21945

# Pittsburgh
lon <- -79.915280
lat <- 40.433810



# Look up latitude and longitude from the zip code
lat.long <- geocode_zip("15217")
lat <- lat.long$lat
lon <- lat.long$lng


# Home: 40 26' 2" N  79 54' 55" W
# 40.43389, -79.91528
lon <- -1* (79 + (54/60) + (55/3600))
lat <- 40 + (26/60) + (2/3600)

# Look up latitude and longitude from the zip code
zip <- 15217
data(zipcode)
lat.long <- zipcode[zipcode$zip==zip,c("latitude","longitude")]
lat <- lat.long[1]
lon <- lat.long[2]

# Home: 40.433810, -79.915280
#       40.433673661058684	-79.91517223628321
#       40.43362	  -79.91536
#       40.4338467, -79.9153318
#       40.43400083686655, -79.91533284458444 <= Google Maps
lon <- -79.91533284458444
lat <- 40.43400083686655


# Pittsburgh
lon <- -79.915280
lat <- 40.433810
```

## get_NWS_data

```{r}
get_NWS_data <- function(lat, lon) {
  myurl <- paste0("https://api.weather.gov/points/",lat,",",lon)
  weather_list <- fromJSON(myurl)
} 
```

## weather_list

```{r}
weather_list <- get_NWS_data(lat,lon)
```

## get_forecast

```{r}
get_forecast <- function(weather_list) {
  sv <- GET(weather_list$properties$forecast)
  forecast <- fromJSON(content(sv, as="text", encoding = "UTF-8"))
  forecast$properties$city <- weather_list$properties$relativeLocation$properties$city
   forecast$properties$state <- weather_list$properties$relativeLocation$properties$state
    forecast$properties$coordinates <- weather_list$properties$relativeLocation$geometry$coordinates
    class(forecast) <- "weather_forecast"
    return(forecast)
}
```

## forecast

```{r}
forecast <- get_forecast(weather_list)
```

## print.weather_forecast

```{r}

print.weather_forecast <- function(forecast, nperiods = NULL) {
  fdb <- forecast$properties$periods
  if (is.null( nperiods)) {
    nperiods <- nrow(fdb)
  }  
  
  start_times <- fdb$startTime
  start_dates <- as.POSIXct(substr(start_times, 1, 19), format="%FT%T")
  end_times <- fdb$endTime
  end_dates <- as.POSIXct(substr(end_times, 1, 19), format="%FT%T")
  
  st0 <- paste0("Forecast for ", forecast$properties$city,", ",
                forecast$properties$state," (",
                forecast$properties$coordinates[2], ", ",
                forecast$properties$coordinates[1], ")")
  cat(st0,"\n\n")
  
  for (j in 1:nperiods) {
    st1 <- paste0(fdb$name[j]," ", format(start_dates[j], "%F"), ": ",
                  fdb$shortForecast[j],"\n")
                  
    cat(st1)
    if (fdb$isDaytime[j]) {
      prefix <- "High: "
    } else {
      prefix <- "Low: "
    }
    st1b <- paste0(prefix,fdb$temperature[j], " ", fdb$temperatureUnit[j],"; ",
                  fdb$windDirection[j]," winds ", fdb$windSpeed[j] ,"\n")
    cat(st1b)
    st2 <- strsplit( fdb$detailedForecast[j], " ")[[1]]
    cat(st2, fill = TRUE)
    cat("\n")
  }
}
```

## Forecast 

```{r, comment=""}
forecast
```

## Forecast table

```{r}
ftbl <- forecast$properties$periods
ftdf <- ftbl %>% select(name, shortForecast) %>% t() %>% data.frame()
names(ftdf) <- ftdf[1,]
ftdf <- ftdf[-1,]
rownames(ftdf) <- NULL
pander(ftdf)
kable(ftdf[,1:6])
```



## Hourly forecast

```{r}
get_hourly_forecast <- function(weather_list) {
  sv <- GET(weather_list$properties$forecastHourly)
  forecast <- fromJSON(content(sv, as="text", encoding = "UTF-8"))
  forecast$properties$city <- weather_list$properties$relativeLocation$properties$city
   forecast$properties$state <- weather_list$properties$relativeLocation$properties$state
    forecast$properties$coordinates <- weather_list$properties$relativeLocation$geometry$coordinates
    class(forecast) <- "hourly_forecast"
    return(forecast)
}

hourly_forecast <- get_hourly_forecast(weather_list)

db <- hourly_forecast$properties$periods
db$Time <- as.POSIXct(db$startTime, format="%FT%T")

tz <- tz_lookup_coords(lat = lat, lon = lon, method = "accurate")

db$NightDay <- as.numeric(db$isDaytime)

db$templab <- as.character(round(db$temperature,0))
db$templab[1:length(db$templab) %% 6 != 1] <- NA

st0 <- paste0("Forecast for ", forecast$properties$city,", ",
                forecast$properties$state," (",
                round(forecast$properties$coordinates[2],3), ", ",
                round(forecast$properties$coordinates[1],3), ")")

db$`wind speed` <- as.numeric(gsub(" mph","",db$windSpeed))
db$windlab <- as.character(db$`wind speed`)
db$windlab[1:length(db$windlab) %% 6 != 1] <- NA

db$shortLab <- db$shortForecast
db$shortLab[1:length(db$shortLab) %% 12 != 1] <- NA

db %>% select(Time, shortLab) %>% filter(!is.na(shortLab))

```

## SunRiseSet

```{r}
SunRiseSet <- function(db, tz, lat, lon) {
  # Change the p.time into the local time zone
  db$p.time <- with_tz(db$Time,tz=tz)
  
  # Sunrise, sunset
  longlat <- matrix(c(lon, lat), nrow=1)
  Hels <- SpatialPoints(longlat, proj4string=CRS("+proj=longlat +datum=WGS84"))
  start.time <- db$p.time[1]
  time.seq <- seq(from=start.time, length.out=9,by='days')
  up <- sunriset(Hels,time.seq,direction='sunrise', POSIXct.out=TRUE)
  down <- sunriset(Hels,time.seq,direction='sunset', POSIXct.out=TRUE)
  up$time <- with_tz(up$time,tz=tz)
  down$time <- with_tz(down$time,tz=tz)
  
  up.time <- up$time[up$time > db$p.time[1]]
  down.time <- down$time[down$time > db$p.time[1]]
  up.time <- up.time[up.time < max(db$p.time)]
  down.time <- down.time[down.time < max(db$p.time)]
  
  up <- data.frame(Date=format(up.time,"%F"),Sunrise=up.time)
  down <- data.frame(Date=format(down.time,"%F"),Sunset=down.time)
  SunriseSunset <- full_join(up, down, by="Date") %>% arrange(Date)
  SunriseSunset$Day <- format(SunriseSunset$Sunrise,"%A")
  SunriseSunset$Day[is.na(SunriseSunset$Day)] <- format(SunriseSunset$Sunset,"%A")
  SunriseSunset <- SunriseSunset %>% select(Date, Day, Sunrise, Sunset)
  SunriseSunset
}

tz <- weather_list$properties$timeZone
tz
SunriseSunset <- SunRiseSet(db=db, tz = tz, lat= lat, lon=lon)
SunriseSunset
```


## Current conditions

/stations/{stationId}/observations/latest

```{r}
get_current_conditions <- function(weather_list, nrows=6) {
  sv <- GET(weather_list$properties$observationStations)
  stations <- fromJSON(content(sv, as="text", encoding = "UTF-8"))
  
  stations_df <- data.frame(ID=stations$features$properties$stationIdentifier,
                            Name=stations$features$properties$name, URL=stations$features$properties$`@id`)
  
  # head(stations_df)
  stations_df$Conditions <- NA
  stations_df$Temperature <- NA
  stations_df$WindChill <- NA
  stations_df$Wind <- NA
  stations_df$WindGusts <- NA
  
  for (i in 1:nrows) {
    sv <- GET(paste0(stations_df$URL[i],"/observations/latest"))
    current <- fromJSON(content(sv, as="text", encoding = "UTF-8"))
    # current$properties$temperature$value
    # current$properties$textDescription
    
    if (!is.null(current$properties$temperature$value)) {
      stations_df$Temperature[i] <- round(32 + (9/5)*current$properties$temperature$value,1)
    }
    stations_df$Conditions[i] <- current$properties$textDescription
    if (!is.null(current$properties$windChill$value)) {
      stations_df$WindChill[i] <- round(32 + (9/5)*current$properties$windChill$value,1)
    }
    if (!is.null(current$properties$windSpeed$value)) {
      stations_df$Wind[i] <- current$properties$windSpeed$value/1.609344
    }
    if (!is.null(current$properties$windGust$value)) {
      stations_df$WindGusts[i] <- current$properties$windGust$value/1.609344
    }
    
  }
  
 # stations_df$Conditions[i] <- current$properties$textDescription
  
  return(stations_df[1:nrows,])
}

current_conditions <- get_current_conditions(weather_list)

current_conditions %>% select(Name, Conditions, Temperature, WindChill, Wind, WindGusts) %>% pander()
```


## NWS plot

```
<img width="95%" src='https://forecast.weather.gov/meteograms/Plotter.php?lat=40.4385&lon=-79.9973&wfo=PBZ&zcode=PAZ021&gset=20&gdiff=10&unit=0&tinfo=EY5&ahour=0&pcmd=11101111110000000000000000000000000000000000000000000000000&lg=en&indu=1!1!1!&dd=&bw=&hrspan=48&pqpfhr=6&psnwhr=6'/></img>
```

```{r}
weather_list$properties$forecastOffice
weather_list$properties$forecastZone
weather_list$properties$relativeLocation$geometry$coordinates

html.str <- paste0("https://forecast.weather.gov/meteograms/Plotter.php?lat=", round(lat,4),"&lon=",round(lon,4),"&wfo=PBZ&zcode=", basename(weather_list$properties$forecastZone),"&gset=20&gdiff=10&unit=0&tinfo=EY5&ahour=0&pcmd=11101111110000000000000000000000000000000000000000000000000&lg=en&indu=1!1!1!&dd=&bw=&hrspan=48&pqpfhr=6&psnwhr=6")
html.str
```



## Temperature

### Landscape

```{r}
pTemp <- ggplot(data = db, aes(x=Time, y=temperature, color = NightDay)) + 
  geom_line(linewidth=1.2) + 
  geom_text(aes(y=temperature,label=templab),vjust=-1) +
  geom_text(aes(y=max(temperature)+30, label=shortLab), color="darkblue", angle=80) +
  scale_x_datetime(labels = date_format("%a %H", tz=tz), breaks="6 hours") +
  xlab("Time") + 
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  theme(legend.position="none") +
  scale_colour_gradient(low="black",high="orange") +
  geom_hline(yintercept = 32, color ="darkblue", lty=2) +
  ggtitle(paste0("Temperature ",st0)) +
  ylim(min(db$temperature),max(db$temperature)+45)

pTemp

pTemp <- pTemp +  
  annotate("rect",xmin=SunriseSunset$Sunrise,xmax=SunriseSunset$Sunset,ymin=-Inf,ymax=max(db$temperature)+2,alpha=1/5,fill="sky blue",colour="black")

pTemp

```

### Portrait

```{r}
vTemp <- ggplot(data = db, aes(y=Time, x=temperature, color=NightDay)) + 
  geom_path() + 
  geom_text(aes(x=temperature,label=templab),vjust=-1) +
  scale_y_datetime(labels = date_format("%a %H", tz=tz), breaks="6 hours") +
  ylab("Time") + 
  theme(legend.position="none") +
  scale_colour_gradient(low="black",high="orange") +
  geom_vline(xintercept = 32, color ="darkblue", lty=2) +
  ggtitle(paste0("Temperature ",st0)) +
  xlim(min(db$temperature),max(db$temperature)+2) +
  coord_y_datetime(ylim = c(max(db$Time), min(db$Time))) +
  scale_x_continuous(breaks= pretty_breaks())

vTemp
```


## Wind speed

```{r}
pWind <- ggplot(data = db, aes(x=Time, y=`wind speed`, color=NightDay)) + 
  geom_line() + 
  geom_text(aes(y=`wind speed`,label=windlab),vjust=-1) +
  scale_x_datetime(labels = date_format("%a %H", tz=tz), breaks="6 hours") +
  xlab("Time") + 
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  theme(legend.position="none") +
  scale_colour_gradient(low="black",high="orange") +
  ggtitle(paste0("Wind Speed ",st0)) +
  ylim(min(db$`wind speed`),max(db$`wind speed`)+1)

pWind
```

## Grid forecast

```{r}
get_grid_forecast <- function(weather_list) {
  sv <- GET(weather_list$properties$forecastGridData)
  forecast <- fromJSON(content(sv, as="text", encoding = "UTF-8"))
  forecast$properties$city <- weather_list$properties$relativeLocation$properties$city
   forecast$properties$state <- weather_list$properties$relativeLocation$properties$state
    forecast$properties$coordinates <- weather_list$properties$relativeLocation$geometry$coordinates
    class(forecast) <- "hourly_forecast"
    return(forecast)
}

grid_forecast <- get_grid_forecast(weather_list)

db.orig <- db
```

## Barometric Pressure

```{r}
 if (length(grid_forecast$properties$pressure$values)>0) {
db <- grid_forecast$properties$pressure[[1]]
db$lab <- as.character(db$value)
db$lab[1:length(db$value) %% 6 != 1] <- NA
db <- dplyr::rename(db, Time=validTime, pressure=value)
db$Time <- as.POSIXct(db$Time, format="%FT%T",tz=tz)
}
```

```{r}
 if (length(grid_forecast$properties$pressure$values)>0) {
pPressure <- ggplot(data = db, aes(x=Time, y=pressure)) + 
  geom_line() + 
  geom_text(aes(y=pressure,label=lab),vjust=-1) +
  scale_x_datetime(labels = date_format("%a %H", tz=tz), breaks="6 hours") +
  xlab("Time") + 
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  theme(legend.position="none") +
  scale_colour_gradient(low="black",high="orange") +
  ggtitle(paste0("Barometric Pressure ",st0)) +
  ylim(min(db$pressure),max(db$pressure)+0.05)
 } else {
   pPressure <- ggplot() +
            annotate("text", x = 2,  y = 2,
                     size = 6,
                     label = "No barometric pressure data available") + theme_void()
}

pPressure
```

## Sky cover

```{r}
db <- grid_forecast$properties$skyCover$values
db$lab <- as.character(db$value)
db$lab[1:length(db$value) %% 6 != 1] <- NA
db <- rename(db, Time=validTime, `sky cover`=value)
db$Time <- as.POSIXct(db$Time, format="%FT%T",tz=tz)
```

### Landscape

```{r}
pSkyCover <- ggplot(data = db, aes(x=Time, y=`sky cover`)) + 
  geom_line() + 
  geom_text(aes(y=`sky cover`,label=lab),vjust=-1) +
  scale_x_datetime(labels = date_format("%a %H", tz=tz), breaks="6 hours") +
  xlab("Time") + 
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  theme(legend.position="none") +
  scale_colour_gradient(low="black",high="orange") +
  ggtitle(paste0("Sky Cover ",st0)) +
  ylim(min(db$`sky cover`),max(db$`sky cover`)+3)

pSkyCover
```

### Tiled heatmap

```{r, fig.width=4}
tmp <- db
tmp$y <- "Sky Cover"
hr <- as.period(ms("60:00"),"hours")
tmp$hj <- rep(c(0.8,0,-0.8), length.out=nrow(db))

hSkyCover <- ggplot(data=tmp, aes(x=y,y=Time,fill=`sky cover`)) + 
  geom_tile(height=3600*6) +
  geom_text_repel(aes(label=lab), size=3, point.size=NA, direction="x", min.segment.length = 10, na.rm=TRUE) +
scale_y_datetime(labels = date_format("%a %H", tz=tz), breaks="6 hours") +
coord_y_datetime(ylim = c(max(tmp$Time), min(tmp$Time))) +
scale_fill_gradient2(low="white", high="darkgray", limits= c(0,100)) +
  theme_minimal() +
  theme(axis.ticks.x=element_blank(),
        axis.title.x = element_blank(),
        axis.line.y = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())

hSkyCover
```


## Probability of precipitation

The Time is returned as

"2023-01-25T06:00:00+00:00/PT1H"

where "PT1H" means an interval with a duration of 1 hour.

By convention, meteorologists use just one time zone: Universal Time, Coordinated (UTC).

```{r}
db <- grid_forecast$properties$probabilityOfPrecipitation$values
db$lab <- as.character(db$value)
db$lab[1:length(db$value) %% 4 != 1] <- NA
db <- rename(db, Time=validTime, `precipitation probability`=value)
db$Time <- as.POSIXct(db$Time, format="%FT%T",tz="UTC")
db$Time <- with_tz(db$Time,tz=tz)

```

### Short-term hourly precipitation forecast

```{r}
SunriseSunset <- SunRiseSet(db=db, tz = tz, lat= lat, lon=lon)

hrs <- c(2:13)
hrs <- which(db[,"Time"] >= Sys.time()) -1
hrs <- hrs[1:24]
pPrecip <- ggplot(data = db[hrs,], aes(x=Time, y=`precipitation probability`)) +
  geom_line() + 
  geom_point() + 
  geom_text(aes(y=`precipitation probability`,label=`precipitation probability`),vjust=-1) +
  scale_x_datetime(labels = date_format("%a %H", tz=tz), breaks="1 hours") + ggtitle("24 hour precipitation forecast") +
  ylim(min(db[hrs,]$`precipitation probability`),max(db[hrs,]$`precipitation probability`)+4) +
            theme(axis.text.x=element_text(angle=45,hjust=1)) + ylim(c(0,100))



pPrecip +
    geom_vline(xintercept = SunriseSunset$Sunset) +
    geom_vline(xintercept = SunriseSunset$Sunrise, col="orange")
```


```{r}
ggplot(data = db[hrs,], aes(x=Time, y=`precipitation probability`)) +
  geom_col(fill="skyblue") +
    geom_text(aes(y=`precipitation probability`,label=`precipitation probability`),vjust=-0.2) +
   scale_x_datetime(labels = date_format("%H", tz=tz), breaks="1 hours") + ggtitle("12 hour precipitation forecast")
```



### Landscape

```{r}
pPrecpProb <- ggplot(data = db, aes(x=Time, y=`precipitation probability`)) + 
  geom_line() + 
  geom_text(aes(y=`precipitation probability`,label=lab),vjust=-1) +
  scale_x_datetime(labels = date_format("%a %H", tz=tz), breaks="6 hours") +
  xlab("Time") + 
  theme(axis.text.x=element_text(angle=45,hjust=1)) +
  theme(legend.position="none") +
  scale_colour_gradient(low="black",high="orange") +
  ggtitle(paste0("Precipitation Prob. ",st0)) +
  ylim(min(db$`precipitation probability`),max(db$`precipitation probability`)+3)

pPrecpProb
```

```{r}
coord_y_datetime <- function(xlim = NULL, ylim = NULL, expand = TRUE) {
  if (!is.null(ylim)) {
    ylim <- lubridate::as_datetime(ylim)
  }
  ggplot2::coord_cartesian(xlim = xlim, ylim = ylim, expand = expand)
}
```

### Portrait


```{r}
vPrecpProb <- ggplot(data = db, aes(y=Time, x=`precipitation probability`)) + 
  geom_path() + 
  geom_text(aes(x=`precipitation probability`,label=lab),vjust=-1) +
  scale_y_datetime(labels = date_format("%a %H", tz=tz), breaks="6 hours") +
  ylab("Time") + 
  theme(legend.position="none") +
  scale_colour_gradient(low="black",high="orange") +
  ggtitle(paste0("Precipitation Prob. ",st0)) +
  xlim(min(db$`precipitation probability`),max(db$`precipitation probability`)+3) +
  coord_y_datetime(ylim = c(max(db$Time), min(db$Time))) +
  scale_x_continuous(breaks= pretty_breaks())

vPrecpProb
```

### Tiled heatmap

```{r, fig.width=4, warning=FALSE, message=FALSE}
tmp <- db
tmp$y <- "Precip. Prob."
hr <- as.period(ms("60:00"),"hours")
tmp$hj <- rep(c(0.8,0,-0.8), length.out=nrow(db))

hPrecipProb <- ggplot(data=tmp, aes(x=y,y=Time,fill=`precipitation probability`)) + 
  geom_tile(height=3600*1) +
  geom_text_repel(aes(label=`precipitation probability`), size=3, point.size=NA, direction="x", min.segment.length = 10, na.rm = TRUE, verbose = FALSE) +
scale_y_datetime(labels = date_format("%a %H", tz=tz), breaks="6 hours") +
coord_y_datetime(ylim = c(max(tmp$Time), min(tmp$Time))) +
scale_fill_gradient2(low="gray", high="blue", limits= c(0,100)) +
  theme_minimal() +
  theme(axis.ticks.x=element_blank(),
        axis.title.x = element_blank(),
        axis.line.y = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())

hPrecipProb
```


# Weather

## Forecast

```{r, echo=FALSE, comment=""}
forecast
```

## Temperature

```{r, echo=FALSE, warning=FALSE}
pTemp
```

## Wind Speed

```{r, echo=FALSE, warning=FALSE}
pWind
```

## Barometric Pressure

```{r, echo=FALSE, warning=FALSE}
pPressure
```

## Sky Cover

```{r, echo=FALSE, warning=FALSE}
pSkyCover
hSkyCover
```

## Precipitation Probability

```{r, echo=FALSE, warning=FALSE}
pPrecpProb
hPrecipProb
```

## Combined plots

```{r, echo=FALSE, warning=FALSE}
pTemp / pPrecpProb 
pSkyCover / pPressure 
pWind 
vTemp 
hPrecipProb | hSkyCover 
```


# Area forecast discussions

Need to know the name of the nearest National Weather Service center.

Looks like that is in `weather_list$properties$cwa`

```
/products/types/{typeId}/locations/{locationId}
```

```{r}
# Get the station name:
weather_list$properties$cwa
sv <- GET("https://api.weather.gov/products/types/AFD/locations")
locations <- fromJSON(content(sv, as="text", encoding = "UTF-8"))
grep("Pittsburgh",locations$locations,value=TRUE)
names(grep("Pittsburgh",locations$locations,value=TRUE))

# Pull list of Area Forecast Discussions
sv <- GET("https://api.weather.gov/products/types/AFD/locations/PBZ")
AFDs <- fromJSON(content(sv, as="text", encoding = "UTF-8"))

# Pull the most recent Area Forecast Discussion
sv <- GET(AFDs$`@graph`$`@id`[1])
currentAFD <- fromJSON(content(sv, as="text", encoding = "UTF-8"))

# Print out the most recent Area Forecast Discussion
cat(currentAFD$productText)
```

# Alerts

```{r}
weather_list$properties$forecastZone
Zone <- basename(weather_list$properties$forecastZone)
Zone
sv <- GET(paste0("https://api.weather.gov/alerts/active/zone/",Zone))
alerts <- fromJSON(content(sv, as="text", encoding = "UTF-8"))

if (length(alerts$features) > 0) {
cat(alerts$features$properties$headline,"\n\n")
# cat("Counties: ",alerts$features$properties$areaDesc,"\n\n")

cat("Counties: ")
writeLines(strwrap(alerts$features$properties$areaDesc, width=70))
cat("\n\n")

nalerts <- length(alerts$features$properties$headline)
nalerts
for (i in 1:nalerts) {
 cat(alerts$features$properties$parameters$NWSheadline[[i]],"\n\n")
 cat(alerts$features$properties$description[i],"\n\n")
}
# cat(alerts$features$properties$description,"\n\n")
# cat(alerts$features$properties$instruction,"\n\n")
}
```


# Session Information

```{r}
sessionInfo()
```

