---
title: "Exploring OGC WMS"
author: "Daniel E. Weeks"
date: "`r format(Sys.time(), '%B %d, %Y, %R')`"
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  html_document:
    df_print: paged
    toc: true
    number_sections: true
    toc_depth: '3'
    code_folding: show
  pdf_document:
    toc: true
    number_sections: true
    toc_depth: 3
#   md_extensions: +raw_attribute
---

```{r,echo=FALSE,message=FALSE,warning=FALSE}
require(knitr)
# Set so that long lines in R will be wrapped:
opts_chunk$set(tidy.opts=list(width.cutoff=80),tidy=TRUE)
```

```{r,echo=FALSE}
# In the event of a crash, save the working space on exit:
save_all <- function() {
  save.image("recover.RData")
}
options(error = save_all)
```


# Load Libraries

```{r load_libraries,message=FALSE}
library(tidyverse)
library(tidylog)
library(sf) # simple features packages for handling vector GIS data
library(httr) # generic webservice package
library(ows4R) # interface for OGC webservices
library(leaflet)
```

# Input directory and files 

```{r}
# Print the working directory
getwd()
```
The input files used in this analysis are ... and can be found in ... 

# Open Geospatial Consortium (OGC) Web Map Service (WMS)

## Links

https://radar.weather.gov/

See

https://inbo.github.io/tutorials/tutorials/spatial_wms_services/

and

https://enterprise.arcgis.com/en/server/latest/publish-services/windows/communicating-with-a-wms-service-in-a-web-browser.htm

Schema:

https://opengeo.ncep.noaa.gov/geoserver/kpbz/ows?service=wms&version=1.3.0&request=GetCapabilities

## NWS GeoServer and GeoWebCache applications

https://opengeo.ncep.noaa.gov/geoserver/www/index.html


Example gist:

https://rstudio-pubs-static.s3.amazonaws.com/573820_deb44ac63243440b972bf6d1845439c9.html

Resources:

https://mesonet.agron.iastate.edu/ogc/

## Example code

```{r}
wfs_bwk <- "https://opengeo.ncep.noaa.gov/geoserver/kpbz/ows?service=wms&version=1.3.0&request=GetCapabilities"
```

```{r}
bwk_client <- WMSClient$new(wfs_bwk)
bwk_client
```

```{r}
bwk_client$getCapabilities()
```
# Example WMS request

http://sampleserver1.arcgisonline.com/ArcGIS/services/Specialty/ESRI_StatesCitiesRivers_USA/MapServer/WMSServer?version=1.3.0&request=GetMap&CRS=CRS:84&bbox=-178.217598,18.924782,-66.969271,71.406235&width=760&height=360&layers=0&styles=default&format=image/png


https://opengeo.ncep.noaa.gov/geoserver/kpbz/ows?SERVICE=WMS&request=GetMap&WIDTH=760&HEIGHT=360&Layers=kpbz_bsrm&Format=image/png&CRS=CRS:84&bbox=-85.218,35.5312,-75.2172,45.532

minx="-85.218" miny="35.5312" maxx="-75.2172" maxy="45.532"


```{r}
# Pittsburgh
lon <- -79.915280
lat <- 40.433810


wms_grb <- "https://opengeo.ncep.noaa.gov/geoserver/kpbz/ows?SERVICE=WMS&request=GetMap&WIDTH=760&HEIGHT=360&Layers=kpbz_bsrm&Format=image/png&CRS=CRS:84&bbox=-85.218,35.5312,-75.2172,45.532"

# WMS link
wms_grb <- "https://opengeo.ncep.noaa.gov/geoserver/kpbz/ows?"
```

# kpbz_bsrm



```{r}
leaflet() %>% 
  addTiles() %>% 
  setView(lng = lon, lat = lat, zoom = 6.8) %>%
  addWMSTiles(
    wms_grb,
    layers = "kpbz_bsrm",
    options = WMSTileOptions(format = "image/png", transparent = TRUE)
  )
```


# kpbz_bdhc

NEXRAD Level 3 Dual-Pol Digital Hydrometeor Classification. This data is provided Multi-Radar-Multi-Sensor (MRMS) algorithm.

```{r}
leaflet() %>% 
  addTiles() %>% 
  setView(lng = lon, lat = lat, zoom = 6.8) %>%
  addWMSTiles(
    wms_grb,
    layers = "kpbz_bdhc",
    options = WMSTileOptions(format = "image/png", transparent = TRUE)
  )
```


# kpbz_bdsa

NEXRAD Level 3 Dual-Pol Digital Storm Total Precipitation. This data is provided Multi-Radar-Multi-Sensor (MRMS) algorithm.

```{r}
leaflet() %>% 
  addTiles() %>% 
  setView(lng = lon, lat = lat, zoom = 6.8) %>%
  addWMSTiles(
    wms_grb,
    layers = "kpbz_bdsa",
    options = WMSTileOptions(format = "image/png", transparent = TRUE)
  )
```

# kpbz_bdzd


# kpbz_bref_raw

NEXRAD Level 2 Super Resolution Radar Base Reflectivity. This data is provided Multi-Radar-Multi-Sensor (MRMS) algorithm.

```{r}
leaflet() %>% 
  addTiles() %>% 
  setView(lng = lon, lat = lat, zoom = 6.8) %>%
  addWMSTiles(
    wms_grb,
    layers = "kpbz_bref_raw",
    options = WMSTileOptions(format = "image/png", transparent = TRUE)
  )
```

# kpbz_bsrm

NEXRAD Level 3 Storm Relative Mean Radial Velocity. This data is provided Multi-Radar-Multi-Sensor (MRMS) algorithm.

```{r}
leaflet() %>% 
  addTiles() %>% 
  setView(lng = lon, lat = lat, zoom = 6.8) %>%
  addWMSTiles(
    wms_grb,
    layers = "kpbz_bsrm",
    options = WMSTileOptions(format = "image/png", transparent = TRUE)
  )
```

# Composite Reflectivity: kpbz_cref

NEXRAD Level 3 Composite Reflectivity. This data is provided Multi-Radar-Multi-Sensor (MRMS) algorithm.

```{r}
leaflet() %>% 
  addTiles() %>% 
  setView(lng = lon, lat = lat, zoom = 6.8) %>%
  addWMSTiles(
    wms_grb,
    layers = "kpbz_cref",
    options = WMSTileOptions(format = "image/png", transparent = TRUE)
  )
```


# Nation-wide composite

Quality Controlled 1km x 1km CONUS Radar Composite Reflectivity. This data is provided Multi-Radar-Multi-Sensor (MRMS) algorithm.

```{r}
ntl_grb <- "https://opengeo.ncep.noaa.gov:443/geoserver/conus/conus_cref_qcd/ows"
```

```{r}
leaflet() %>% 
  addTiles() %>% 
  setView(lng = lon, lat = lat, zoom = 5) %>%
  addWMSTiles(
    ntl_grb,
    layers = "conus_cref_qcd",
    options = WMSTileOptions(format = "image/png", transparent = TRUE)
  )
```


# Time-enabled national view

This service is time-enabled, meaning clients can submit image requests including a time parameter specified in epoch time format (milliseconds since 00:00 January 1, 1970).The time extent of this service includes the past four hours up to the current time updated approximately every ten minutes. All times are specifed in UTC. If time parameters are omitted, the most recent image will be returned.

```{r}
ntl_time_grb <- "https://idpgis.ncep.noaa.gov/arcgis/services/radar/radar_base_reflectivity_time/ImageServer/WMSServer"
```

```{r}
leaflet() %>% 
  addTiles() %>% 
  setView(lng = lon, lat = lat, zoom = 4) %>%
  addWMSTiles(
    ntl_time_grb,
    layers = "radar_base_reflectivity_time",
    options = WMSTileOptions(format = "image/png", transparent = TRUE)
  )
```

# mesonet

Based on example code from this gist:

https://rstudio-pubs-static.s3.amazonaws.com/573820_deb44ac63243440b972bf6d1845439c9.html


```{r}
athens <- leaflet() %>%
        addProviderTiles(providers$OpenStreetMap) %>%
        setView(lat=lat, lng=lon, zoom = 4)
athens %>% addWMSTiles(
  "http://mesonet.agron.iastate.edu/cgi-bin/wms/nexrad/n0r.cgi",
  layers = "nexrad-n0r-900913",
  options = WMSTileOptions(format = "image/png", transparent = TRUE),
  attribution = "Weather data © 2020 IEM Nexrad"
)
```

## nexrad-n0q-900913-m05m

```{r}
athens <- leaflet() %>%
        addProviderTiles(providers$OpenStreetMap) %>%
        setView(lat=lat, lng=lon, zoom = 4)
athens %>% addWMSTiles(
  "http://mesonet.agron.iastate.edu/cgi-bin/wms/nexrad/n0r.cgi",
  layers = "nexrad-n0r-900913-m05m",
  options = WMSTileOptions(format = "image/png", transparent = TRUE),
  attribution = "Weather data © 2020 IEM Nexrad"
)
```

## nexrad-n0q-900913-m20m

```{r}
athens <- leaflet() %>%
        addProviderTiles(providers$OpenStreetMap) %>%
        setView(lat=lat, lng=lon, zoom = 4)
athens %>% addWMSTiles(
  "http://mesonet.agron.iastate.edu/cgi-bin/wms/nexrad/n0r.cgi",
  layers = "nexrad-n0r-900913-m20m",
  options = WMSTileOptions(format = "image/png", transparent = TRUE),
  attribution = "Weather data © 2020 IEM Nexrad"
)
```


## nexrad-n0q-900913-m55m

```{r}
athens <- leaflet() %>%
        addProviderTiles(providers$OpenStreetMap) %>%
        setView(lat=lat, lng=lon, zoom = 4)
athens %>% addWMSTiles(
  "http://mesonet.agron.iastate.edu/cgi-bin/wms/nexrad/n0r.cgi",
  layers = "nexrad-n0r-900913-m50m",
  options = WMSTileOptions(format = "image/png", transparent = TRUE),
  attribution = "Weather data © 2020 IEM Nexrad"
)
```

# Session Information

```{r}
sessionInfo()
```

